---
title: "Assignment 10"
author: "Nhu Ho"
date: "2025-06-01"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(meta)
library(dplyr)
library(ggplot2)
```

## 1. Load and Inspect the Data

```{r}
data <- read_excel("/Users/hoangnhu/Downloads/metaanalysis_data.xlsx")
head(data)
str(data)
```

## 2. Meta-analysis: Calculating Effect Sizes

I assume boys are the experimental group and girls the control group.

```{r}
m <- metacont(n.e = data$N_boys,
                   mean.e = data$Mean_boys_play_male,
                   sd.e = data$SD_boys_play_male,
                   n.c = data$N_girls,
                   mean.c = data$Mean_girls_play_male,
                   sd.c = data$SD_girls_play_male,
                   data = data,
                   studlab = data$Study,
                   common = TRUE,
                   random = TRUE)
summary(m)

```

## 3. Forest Plot

```{r}
m %>% forest(sortvar=TE)
```

## 4. Funnel Plot (Basic)

```{r}
m %>% funnel()
```

## 5. Funnel Plot (Contour-enhanced)

```{r}
contour_levels <- c(0.90, 0.95, 0.99)
contour_colors <- c("darkblue", "blue", "lightblue")
funnel(m, contour = contour_levels, col.contour = contour_colors)
legend("topright", c("p < 0.10", "p < 0.05", "p < 0.01"), bty = "n", fill = contour_colors)
```

## 6. Meta-regression: Does Method or Quality Affect Results?

```{r}
# Replace these with correct variable names from your dataset
m %>% metareg(~ `Neutral toys` + `Parent present` + Setting + `NOS score`)
```

## 7. Meta-regression: Does Author Gender Affect the Results?

```{r}
m$data$Author_gender_ratio <- m$data$`Female authors` / 
  (m$data$`Female authors` + m$data$`Male authors`)

m %>% metareg(~ Author_gender_ratio)
```

## 8. Interpretation

- Combined Effects:
  - The combined result using a random-effects model showed a statistically significant difference (MD = 94.78, p < 0.0001), with boys exhibiting higher play behavior scores.
  - There was very high heterogeneity among the studies (I^2 = 88.0%).

- Forest Plot:
  - The forest plot shows the Mean Difference (MD) for each study and the overall combined result. It illustrates considerable variation in results across individual studies.

- Funnel Plot:
  - The funnel plot showed asymmetry, suggesting potential publication bias or other factors contributing to heterogeneity. Studies appeared to be more concentrated on the side with positive and statistically significant results.

- Meta-regression: Effect of Methods/Quality:
  - Study methodology and quality factors (NOS score) explained a portion of the heterogeneity (approximately 22.69%).
  - Specifically, the presence of Neutral toys and the NOS score (study quality score) significantly influenced the results.

- Meta-regression: Effect of Author Gender:
  - The gender ratio of authors did not significantly affect the study results (p = 0.7416).

## References
- Using the assignment 10 of teacher's code
- Using ChatGPT to fix my error code for part 7